Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-08-28 paper.Rnw
Jason's comments mostly responded to.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: 
%  - check tense: we are is have has 
%  - update montages with TAL coordinates
%  - add MAGeT brain diagram, and remove pseudocode
% Sweave/Knitr init
<<setup, include=FALSE, cache=FALSE>>=
library(knitr)
opts_chunk$set(echo = FALSE, 
               message = FALSE, 
               warning = FALSE, 
               fig.align = 'center', 
               tidy = FALSE, 
               comment = NA, 
               cache = TRUE,
               fig.width = 6, 
               fig.height = 6)
library(ggplot2)
library(Hmisc)
library(reshape2)
library(ADNIMERGE)
library(plyr)
options(digits=3)
theme_set(theme_bw(base_size = 12))

@@

There are few methods that have attempted to perform multi-atlas segmentation
with a limited number of input atlases. The LEAP algorithm is an elegant
modification to the basic multi-atlas strategy \citep{Wolz2010} in which the
atlas library is grown, beginning with a set of manually labelled atlases, and
successively incorporating unlabelled target images after themselves being
labelled using multi-atlas techniques. The sequence in which target images are
labelled is chosen so that the similarity between the atlas images and the
target images is minimised at each step, effectively allowing for deformations
between very dissimilar images to be broken up into sequences of smaller
deformations. Although \citet{Wolz2010} begin with an atlas library of 30 MR
images, this method could theoretically work using a much smaller atlas library.
In their validation, LEAP was used to segment the whole hippocampus in the
ADNI-1 baseline dataset, achieving a mean Dice score of 0.85 with manual
segmentations.

To the best of our knowledge there are only two other segmentation methods that
attempt to define the hippocampus and its subfields using standard T1-weighted
data. The first is included with the FreeSurfer package \citep{VanLeemput2009}.
This work is limited as it omits the tail of the hippocampus and the
segmentation protocol has yet to be fully validated. Nonetheless, it
demonstrates that the applicability of hippocampal subfield segmentation using
data from 10 subjects. In the second method, \citet{Yushkevich2009} hippocampal
subfields were acquired and labelled on high-resolution MRI data from post-mortem
medial temporal lobe samples. Using nonlinear registration guided by manually
derived hippocampus masks and specific landmarks, the authors demonstrated
accurate parcellation of hippocampal subfields in unlabelled MRI volumes.

@@

\subsection{The \mb Algorithm}
In this paper, we will use the term {\em label} to mean any segmentation (manual or 
derived) of an MR image. {\em Label propagation}, or {\em labelling}, is the 
process by which two images are registered and the resulting transformation 
is applied to the labels from one image to bring them into alignment with the 
other image. We will use the term {\em atlas} to mean a manually segmented image,
and the term {\em template} to mean an automatically segmented image (i.e. 
via label propagation). The terms {\em atlas library} and {\em template library} 
describe any set of such images. Additionally, we will use the term {\em target} 
to refer to an unlabelled image that is undergoing segmentation.

The simplest form of multi-atlas segmentation, (which we will call {\em basic 
multi-atlas segmentation}), involves three steps. First, each labelled 
input image (i.e. atlas or template) is registered to an unlabelled target image.
Second, the labels from each image are propagated to the target image space. 
Third, the labels are combined into a single label by label fusion
\citep{Heckemann2006, Heckemann2011}. This method is described in detail in
other publications \citep{Collins2010,Heckemann2011,Aljabar2009}.

@@

\paragraph{Label fusion methods}
Label fusion is a term given to the process of combining the information from
several candidate labellings for an intensity image into a single labelling.  In
this experiment we explore three fusion methods. 
\begin{description}
  \item[Voxel-wise Majority Vote]
  Labels are propagated from all template library images to a target.  Each
  output voxel is given the most frequent label at that voxel location amongst
  all candidate labellings.

@@

\paragraph{Winterburn Atlases dataset} 
The Winterburn atlases \citep{Winterburn2013} are digital hippocampal
segmentations of five in-vivo $300\mu$ isotropic T1-weighted MR images. The
segmentations include subfield segmentations for the cornus ammonis (CA) 1, CA4,
dentate gyrus, subiculum, and CA 2 and 3 combined. Subjects in the Winterburn
atlases range in age from 29-57 years (mean age of 37), and include two males
and three females.

@@

In part 2a of this experiment, we have modified the LOOCV experimental
design in order to compare \mb segmentation accuracy with the accuracy of image
resampling error. The five $300\mu$-isotropic voxel Winterburn atlas images and
labels are used as the atlas library, and LOOCV is conducted using the five Winterburn
atlas images subsampled (using trilinear interpolation) to
0.9mm-isotropic voxel resolution (referred to as the {\em Subsampled} dataset)
as input subjects. Subsampling the subject images allows us to assess \mb in a
typical segmentation scenario (high-resolution atlases and lower-resolution
subjects).  The template library is composed of all five subject images, plus an
additional set of 3T T1 images (0.9mm-isotropic voxels) of healthy subjects
acquired separately (Table \ref{tab:WAval-healthy-demographics}). The optimal
size of template library, registration method, and label fusion method found in
Experiment 1 are used.  As with traditional LOOCV, each subject image is
segmented by \mb with that subject's image excluded from the atlas library.  In
part 2b of this experiment, we carry out a similar validation in which the
subject images are separately acquired T1 BRAVO images of four of the five
Winterburn atlas subjects (referred to as the {\em BRAVO} dataset).  Figure
\ref{fig:LOOCV-schematic} illustrates the experimental set up of both parts of
this experiment.

@@

To validate that \mb works effectively in the context of other neuropsychiatric
disorders, in this experiment we use the Winterburn atlases to predict the
hippocampal segmentations of patients with Schizophrenia. The resulting
segmentations are assessed for quality by comparison with expert manual
segmentations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-COMPLETE
% Prepares the data in the form needed for plotting.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
<<ADNI-volumes-prep,echo=F,cache=T>>=
means.complete   <- read.csv(gzfile('data/cache/ADNI1:means.complete.csv.gz'))
package_totals   <- read.csv(gzfile('data/cache/ADNI1:package_totals.csv.gz'))
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: mean Kappa plot by atlases, templates, reg and voting method. 
\begin{figure}
<<fig:ADNI1-xval-k-mean, cache=TRUE, dependson='ADNI1-xval-prep', fig.width=7, fig.height=7>>=
stderr <- function(x) sqrt(var(x)/length(x))
ggplot(subset(all_data_mean, (templates.mb*atlases) %% 2 == 1),
       aes(x=templates.mb,y=k.mb, colour=as.factor(atlases))) + #as.factor((atlases*templates.mb) %% 2 ))) + 
  facet_grid(reg_method~method.mb) + 
  stat_summary(fun.y=mean,geom='line',
               aes(y=k.mb, weight=1, group=as.factor(atlases))) + 
  stat_summary(fun.y=mean,
               fun.ymin=function (x) mean(x) - stderr(x),
               fun.ymax=function (x) mean(x) + stderr(x), 
               geom='errorbar',
               aes(y=k.mb, weight=1, group=as.factor(atlases)), width=0.5) + 
  #stat_smooth(method='lm', formula=y~log(x)) + 
  scale_colour_hue(name="Number of Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean DSC" ) + 
  opts(legend.direction = "horizontal", legend.position = "bottom", 
        axis.text = element_text(size = 8))
@
  \caption{Mean Dice's Similarity Coefficient of \mb segmentations with 
  SNT \gs segmentations for 69 ADNI1 subjects vs. atlas and template library
  size, registration algorithm, and label fusion method. Points above zero
  indicate \mb parameter settings yielding a higher mean DSC score than
  multi-atlas segmentation using the same number of atlases.
  \label{fig:ADNI1-xval-k-mean}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: "increase" in mean kappa over multi-atlas
\begin{figure}
<<fig:ADN11-xval-k-diff,cache=TRUE,dependson='ADNI1-xval-prep'>>=
ggplot(subset(all_data_mean, reg_method=="ANTS" & 
                method.mb=="Majority Vote" & (templates.mb*atlases) %% 2 == 1), 
       aes(x=templates.mb, y=k_diff, colour=as.factor(atlases))) + 
  #facet_grid(reg_method~method.y) + 
  stat_summary(fun.data=mean_cl_boot,geom='errorbar',
               aes(y=k_diff,colour=as.factor(atlases), width=0.2)) +
  stat_summary(fun.y=mean, geom="point", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  stat_summary(fun.y=mean, geom="line", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  #stat_smooth(method=lm, formula=y~log(x)) + 
  geom_hline(aes(alpha=0.5, yintercept=0), linetype='dashed') + 
  scale_x_continuous(breaks=seq(1,20,2)) + scale_y_continuous(breaks=seq(-1,1,by=0.01)) + 
  scale_colour_hue(name="Number of Atlases") +
  scale_alpha_continuous(guide = "none") + 
  scale_linetype_discrete(guide = "none") + 
  xlab( "Number of Templates" ) + 
  ylab( "Difference in mean DSC" ) +
  opts(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{Difference in mean Dice's Similarity Coefficient of \mb and
  multi-atlas segmentations with \gs (SNT) segmentations for a range of atlas
  and template library sizes. \label{fig:ADNI1-xval-k-diff}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

casted = dcast(mean_sz_vols, Subject ~ Method, value.var = "Volume")
lm = lm(MAGeT ~ Manual, casted)
ggplot(data=casted, aes(x = Manual, y = MAGeT)) + 
  geom_smooth(method="lm", formula=y~x) + 
  geom_point() + 
  geom_text(aes(x=3500, y=5000, label=lm_eqn(lm),hjust=0,size=1), parse=TRUE, data=data.frame()) +
  xlab(expression("Mean Manual hippocampus volume " (mm^3))) + 
  ylab(expression("Mean MAGeT hippocampus volume "  (mm^3))) + 
  scale_size_continuous(guide="none") 
@
  \caption{Subject mean hippocampal volumes by \mb vs. manually segmented
   volumes from the First Episode Patients with Schizophrenia dataset. A linear fit
   and standard error are shown.}
  \label{fig:SZ-volumes}
\end{figure}

@@

ggplot(data=melted, aes(x=SNT, y=volume, colour=Method)) + 
    geom_point(size=1) + 
    geom_smooth(method="lm") + 
    xlab(expression("SNT \\gs hippocampal volume " (mm^3))) + 
    ylab(expression("Automated hippocampal volume " (mm^3))) +
    annotate("text", y = c(2000,1500,1000,500), x=Inf-100, size=2.5,
              label = c(paste("FS r =", round(cor(df$SNT, df$FS),2)),
                        paste("FSL r =", round(cor(df$SNT, df$FSL),2)),
                        paste("MAPER r =", round(cor(df$SNT, df$MAPER),2)),
                        paste("MAGeT r =", round(cor(df$SNT, df$MAGeT),2))),
              hjust=1.1,vjust=1.5) +
    opts(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{Subject mean hippocampal volume as measured in the \adnidataset
dataset by each of the four automated methods investigated (FreeSurfer (FS),
FSL, MAPER, \mb) vs. SNT \gs. Linear fit lines and pearson
correlations are shown for each method.}
  \label{fig:ADNI-volumes-plot}
\end{figure}

>>>>

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: 
%  - check tense: we are is have has 
%  - update montages with TAL coordinates
%  - add MAGeT brain diagram, and remove pseudocode
% Sweave/Knitr init
<<setup, include=FALSE, cache=FALSE>>=
library(knitr)
opts_chunk$set(echo = FALSE, 
               message = FALSE, 
               warning = FALSE, 
               fig.align = 'center', 
               tidy = FALSE, 
               comment = NA, 
               cache = TRUE,
               fig.width = 6, 
               fig.height = 6)
library(ggplot2)
library(Hmisc)
library(reshape2)
library(ADNIMERGE)
library(plyr)
options(digits=3)
theme_set(theme_bw(base_size = 12))

@@

Of special relevance to the present work is the LEAP algorithm \citep{Wolz2010}
because of its focus on performing multi-atlas segmentation with a limited
number of input atlases.  The LEAP algorithm is a clever modification to the
basic multi-atlas strategy in which an atlas library is grown, beginning with a
set of manually labelled atlases, by successively incorporating unlabelled
target images once they themselves have been labelled using multi-atlas
techniques. The sequence in which target images are labelled is chosen so that
the similarity between the atlas images and the target images is minimised at
each step, effectively allowing for deformations between very dissimilar images
to be broken up into sequences of smaller deformations. Although
\citet{Wolz2010} begin with an atlas library of 30 MR images, this method could
theoretically work using a much smaller atlas library.  In their validation,
LEAP was used to segment the whole hippocampus in the ADNI-1 baseline dataset,
achieving a mean Dice score of 0.85 against \gs segmentations.

To the best of our knowledge there are only two automated segmentation methods
that attempt to define the hippocampus and its subfields using standard
T1-weighted data. The first is included with the FreeSurfer package
\citep{VanLeemput2009}.  This work is limited as it omits the tail of the
hippocampus and the segmentation protocol has yet to be fully validated.
Nonetheless, it demonstrates that the applicability of hippocampal subfield
segmentation using data from 10 subjects. In the second method,
\citet{Yushkevich2009} hippocampal subfields were acquired and labelled on
high-resolution MRI data from post-mortem medial temporal lobe samples. Using
nonlinear registration guided by manually derived hippocampus masks and specific
landmarks, the authors demonstrated accurate parcellation of hippocampal
subfields in unlabelled MRI volumes.

@@

\subsection{The \mb Algorithm}
In this paper, we will use the term {\em label} to mean any segmentation (manual or 
derived) of an MR image. {\em Label propagation} is the process by which two
images are registered and the resulting transformation is applied to the labels
from one image to bring them into alignment with the other image. We will use
the term {\em atlas} to mean a manually segmented image, and the term {\em
template} to mean an automatically segmented image (i.e.  via label
propagation). The terms {\em atlas library} and {\em template library} describe
any set of such images. Additionally, we will use the term {\em target} to refer
to an unlabelled image that is undergoing segmentation.

The simplest form of multi-atlas segmentation, (which we will call {\em basic 
multi-atlas segmentation}), involves three steps. First, each labelled 
input image (i.e. atlas or template) is registered to an unlabelled target image.
Second, the labels from each image are propagated to the target image space. 
Third, the labels are combined into a single label by label fusion
\citep{Heckemann2006, Heckemann2011}. This method is described in detail in
other publications \citep{Collins2010,Heckemann2011,Aljabar2009}. When only a
single atlas is used, basic multi-atlas segmentation degenerates into
model-based segmentation: labels are propogated from the atlas to a target, and
no label fusion is needed.

@@

\paragraph{Label fusion methods}
Label fusion is a term given to the process of combining the information from
several candidate labels for an intensity image into a single labelling.  In
this experiment we explore three fusion methods. 
\begin{description}
  \item[Voxel-wise Majority Vote]
  Labels are propagated from all template library images to a target.  Each
  output voxel is given the most frequent label at that voxel location amongst
  all candidate labels.

@@

\paragraph{Winterburn Atlases dataset} 
The Winterburn atlases \citep{Winterburn2013} are digital hippocampal
segmentations of five in-vivo $300\mu$ isotropic T1-weighted MR images. The
segmentations include subfield segmentations for the cornu ammonis (CA) 1, CA4,
dentate gyrus, subiculum, and CA 2 and 3 combined. Subjects in the Winterburn
atlases range in age from 29-57 years (mean age of 37), and include two males
and three females.

@@

In part 2a of this experiment, we have modified the LOOCV experimental
design in order to compare \mb segmentation accuracy with the accuracy of image
resampling error. The five $0.3mm$-isotropic voxel Winterburn atlas images and
labels are used as the atlas library, and LOOCV is conducted using the five Winterburn
atlas images subsampled (using trilinear interpolation) to
0.9mm-isotropic voxel resolution (referred to as the {\em Subsampled} dataset)
as input subjects. Subsampling the target images allows us to assess \mb in a
typical segmentation scenario (high-resolution atlases and lower-resolution
subjects).  The template library is composed of all five subject images, plus an
additional set of 3T T1 images (0.9mm-isotropic voxels) of healthy subjects
acquired separately (Table \ref{tab:WAval-healthy-demographics}). The optimal
size of template library, registration method, and label fusion method found in
Experiment 1 are used.  As with traditional LOOCV, each subject image is
segmented by \mb with that subject's image excluded from the atlas library.  In
part 2b of this experiment, we carry out a similar validation in which the
subject images are separately acquired T1 BRAVO images of four of the five
Winterburn atlas subjects (referred to as the {\em BRAVO} dataset).  Figure
\ref{fig:LOOCV-schematic} illustrates the experimental set up of both parts of
this experiment.

@@

To validate that \mb works effectively in the context of other neurological
disorders, in this experiment we use the Winterburn atlases to predict the
hippocampal segmentations of patients with Schizophrenia. The resulting
segmentations are assessed for quality by comparison with expert manual
segmentations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-COMPLETE
% Prepares the data in the form needed for plotting.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
<<ADNI-volumes-prep,echo=F,cache=T>>=
means.complete   <- read.csv('data/cache/ADNI1:qc.csv')
package_totals   <- read.csv('data/cache/ADNI1:package_totals.csv')
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: mean Kappa plot by atlases, templates, reg and voting method. 
\begin{figure}
<<fig:ADNI1-xval-k-mean, cache=TRUE, dependson='ADNI1-xval-prep', fig.width=7, fig.height=7>>=
stderr <- function(x) sqrt(var(x)/length(x))
ggplot(subset(all_data_mean, (templates.mb*atlases) %% 2 == 1),
       aes(x=templates.mb,y=k.mb, colour=as.factor(atlases))) + #as.factor((atlases*templates.mb) %% 2 ))) + 
  facet_grid(reg_method~method.mb) + 
  stat_summary(fun.y=mean,geom='line',
               aes(y=k.mb, weight=1, group=as.factor(atlases))) + 
  stat_summary(fun.y=mean,
               fun.ymin=function (x) mean(x) - stderr(x),
               fun.ymax=function (x) mean(x) + stderr(x), 
               geom='errorbar',
               aes(y=k.mb, weight=1, group=as.factor(atlases)), width=0.5) + 
  #stat_smooth(method='lm', formula=y~log(x)) + 
  scale_colour_hue(name="Number of Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean DSC" ) + 
  opts(legend.direction = "horizontal", legend.position = "bottom", 
        axis.text = element_text(size = 8))
@
  \caption{Mean Dice's Similarity Coefficient of \mb segmentations with 
  SNT \gs segmentations for 69 ADNI1 subjects vs. atlas and template library
  size, registration algorithm, and label fusion method. Points above zero
  indicate \mb parameter settings yielding a higher mean DSC score than
  multi-atlas segmentation using the same number of atlases. Error bars
  indictate standard error.
  \label{fig:ADNI1-xval-k-mean}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: "increase" in mean kappa over multi-atlas
\begin{figure}
<<fig:ADN11-xval-k-diff,cache=TRUE,dependson='ADNI1-xval-prep'>>=
ggplot(subset(all_data_mean, reg_method=="ANTS" & 
                method.mb=="Majority Vote" & (templates.mb*atlases) %% 2 == 1), 
       aes(x=templates.mb, y=k_diff, colour=as.factor(atlases))) + 
  #facet_grid(reg_method~method.y) + 
  stat_summary(fun.data=mean_cl_boot,geom='errorbar',
               aes(y=k_diff,colour=as.factor(atlases), width=0.2)) +
  stat_summary(fun.y=mean, geom="point", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  stat_summary(fun.y=mean, geom="line", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  #stat_smooth(method=lm, formula=y~log(x)) + 
  geom_hline(aes(alpha=0.5, yintercept=0), linetype='dashed') + 
  scale_x_continuous(breaks=seq(1,20,2)) + scale_y_continuous(breaks=seq(-1,1,by=0.01)) + 
  scale_colour_hue(name="Number of Atlases") +
  scale_alpha_continuous(guide = "none") + 
  scale_linetype_discrete(guide = "none") + 
  xlab( "Number of Templates" ) + 
  ylab( "Difference in mean DSC" ) +
  opts(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{Difference in mean Dice's Similarity Coefficient of \mb and
  multi-atlas segmentations with \gs (SNT) segmentations for a range of atlas
  and template library sizes. Error bars indicate standard error.
  \label{fig:ADNI1-xval-k-diff}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

casted = dcast(mean_sz_vols, Subject ~ Method, value.var = "Volume")
lm = lm(MAGeT ~ Manual, casted)
ggplot(data=casted, aes(x = Manual, y = MAGeT)) + 
  geom_smooth(method="lm", formula=y~x) + 
  geom_point() + 
  geom_text(aes(x=3500, y=5000, label=lm_eqn(lm),hjust=0,size=1), parse=TRUE, data=data.frame()) +
  xlab(expression("Mean Manual hippocampus volume " (mm^3))) + 
  ylab(expression("Mean MAGeT hippocampus volume "  (mm^3))) + 
  scale_size_continuous(guide="none") 
@
  \caption{Mean hippocampus volume as measured by \mb  vs. manually segmented
  volumes from the First Episode Patients with Schizophrenia dataset. A linear
  fit line is shown, with shaded region showing standard error. }
  \label{fig:SZ-volumes}
\end{figure}

@@

levels(melted$Method) = c("FS"    = "FreeSurfer", 
                          "FSL"   = "FSL", 
                          "MAPER" = "MAPER", 
                          "MAGeT" = "MAGeT")

ggplot(data=melted, aes(x=SNT, y=volume, colour=Method)) + 
    geom_point(size=1) + 
    geom_smooth(method="lm") + 
    xlab(expression("SNT \\gs mean hippocampus volume " (mm^3))) + 
    ylab(expression("Automated mean hippocampal volume " (mm^3))) +
    annotate("text", y = c(2000,1500,1000,500), x=Inf-100, size=2.5,
              label = c(paste("FS r =", round(cor(df$SNT, df$FS),2)),
                        paste("FSL r =", round(cor(df$SNT, df$FSL),2)),
                        paste("MAPER r =", round(cor(df$SNT, df$MAPER),2)),
                        paste("MAGeT r =", round(cor(df$SNT, df$MAGeT),2))),
              hjust=1.1,vjust=1.5) +
    opts(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{Subject mean hippocampal volume as measured in the \adnidataset
dataset by each of the four automated methods investigated (FreeSurfer (FS),
FSL, MAPER, \mb) vs. SNT \gs. Linear fit lines and pearson
correlations are shown for each method.}
  \label{fig:ADNI-volumes-plot}
\end{figure}
